Syntax and Semantics of Abstract Binding Trees

### 2015-11-24 paper.tex
require satisfaction of glueing condition for operators

We will write $\IsOperator{\Upsilon}{\vartheta}{a}$ in case
$\Member{\vartheta}{\Operators\Pair{\Upsilon}{a}}$ and note that this judgment
enjoys the structural properties of weakening and exchange via functoriality of
$\Operators$. Operators $\vartheta_{0}, \ldots, \vartheta_{n}$ are defined by
specifying the fibers of
$\Of{\pi_{\Operators}}{\Grothendieck{}{\Operators}\ra\SCtx\times\Discrete{\Arities}}$
in which they reside:
\begin{alignat*}{3}
  \null
&
  \IMode{{\pi_{\Operators}}^{-1}{\Pair{\Upsilon}{a}}}
&&
  \,\mathrel{\ {{:}}}\,
&&
  \IMode{\SCtx\times\Discrete{\Arities}\ra\Sets}
\\
  \null
&
  \IMode{{\pi_{\Operators}}^{-1}{\Pair{\Upsilon}{a}}}
&&
  \,=\,\
&&
    \OMode{
      \MkSet{
        \vartheta\in\Pair{\Upsilon}{a}
        \mid{\pi_{\Operators}}{\Pair{\Pair{\Upsilon}{a}}{\vartheta}} =
        \Pair{\Upsilon}{a}
      }
    }
\end{alignat*}

>>>>

We will write $\IsOperator{\Upsilon}{\vartheta}{a}$ in case
$\Member{\vartheta}{\Operators\Pair{\Upsilon}{a}}$ and note that this judgment
enjoys the structural properties of weakening and exchange via functoriality of
$\Operators$. Operators $\vartheta_{0}, \ldots, \vartheta_{n}$ are defined by
specifying the fibers of
$\Of{\pi_{\Operators}}{\Grothendieck{}{\Operators}\ra\SCtx\times\Discrete{\Arities}}$
in which they reside, such that the glueing condition is satisfied:
\begin{alignat*}{3}
  \null
&
  \IMode{{\pi_{\Operators}}^{-1}{\Pair{\Upsilon}{a}}}
&&
  \,\mathrel{\ {{:}}}\,
&&
  \IMode{\SCtx\times\Discrete{\Arities}\ra\Sets}
\\
  \null
&
  \IMode{{\pi_{\Operators}}^{-1}{\Pair{\Upsilon}{a}}}
&&
  \,=\,\
&&
    \OMode{
      \MkSet{
        \vartheta\in\Pair{\Upsilon}{a}
        \mid{\pi_{\Operators}}{\Pair{\Pair{\Upsilon}{a}}{\vartheta}} =
        \Pair{\Upsilon}{a}
      }
    }
\end{alignat*}
